survey-analysis-final

### 2021-04-21 dataset/survey-results-final.Rmd
Added a few lines to dataset/survey-results-final.Rmd in order for it to also report the 95% confidence interval.

```{r}

chiTest <- c()
oddsRatio <- c()
oddsRatioTest <- c()
mannWhitneyTest <- c()
cliffDelta <- c()

for(i in 1:10){
  subSet <- ds[is.element(el = ds$qid, set = c(i,i+10)),]
  print(atomDescription[i])

@@

  chiTest[i] <- format.pval(test$p.value) 
  oddsRatio[i] <- odds.ratio(tableCorrectness)$OR
  oddsRatioTest[i] <- format.pval(odds.ratio(tableCorrectness)$p)

@@

  mod <- glm(subSet$correct ~ subSet$atom +  experience,family="binomial")
  print(summary(mod))
  print(prop.table(table(subSet$correct,subSet$experience),margin = 2))
}

analysis_df <- data.frame(atomDescription, chiTest, oddsRatio, oddsRatioTest, mannWhitneyTest, cliffDelta)
analysis_df <- analysis_df[order(-oddsRatio),]

colnames(analysis_df) <- c("Atom", "ChiTest", "Odds Ratio Correctness", "p-value", "Wilcox Test (Time)", "Cliff Delta")

analysis_df

xtable(analysis_df)
```

>>>>

```{r}
chiTest <- c()
oddsRatio <- c()
oddsRatioTest <- c()
ci25 <- c()
ci975 <- c()
mannWhitneyTest <- c()
cliffDelta <- c()
for(i in 1:10){
  subSet <- ds[is.element(el = ds$qid, set = c(i,i+10)),]
  print(atomDescription[i])

@@

  chiTest[i] <- format.pval(test$p.value) 
  oddsRatio[i] <- odds.ratio(tableCorrectness)$OR
  oddsRatioTest[i] <- format.pval(odds.ratio(tableCorrectness)$p)
  ci25[i] <- odds.ratio(tableCorrectness, level=0.95)$"2.5 %"
  ci975[i] <- odds.ratio(tableCorrectness, level=0.95)$"97.5 %"

@@

  mod <- glm(subSet$correct ~ subSet$atom +  experience,family="binomial")
  print(summary(mod))
  print(prop.table(table(subSet$correct,subSet$experience),margin = 2))
}
analysis_df <- data.frame(atomDescription, chiTest, oddsRatio, oddsRatioTest, ci25, ci975, mannWhitneyTest, cliffDelta)
analysis_df <- analysis_df[order(-oddsRatio),]
colnames(analysis_df) <- c("Atom", "ChiTest", "Odds Ratio Correctness", "p-value", "CI 2.5%", "CI 97.5%", "Wilcox Test (Time)", "Cliff Delta")
analysis_df
xtable(analysis_df)
```
